### 2019-05-28 doc/chapters/using_bitcoins.tex
added language=scala

The relevant parts for the property to be verified are the following two lines.
\begin{lstlisting}
  val prevOutputTxIds = transaction.inputs.map(_.previousOutput.txId)
  val noDuplicateInputs = prevOutputTxIds.distinct.size == prevOutputTxIds.size
\end{lstlisting}
It gathers all inputs output transaction ids.
On this previous outputs ids it calls distinct and checks if the size stays the same.
Distinct removes duplicates, so if there was two times the same input transaction id the size of those ids would be greater before calling distinct.

>>>>

The relevant parts for the property to be verified are the following two lines.
\begin{lstlisting}[language=scala]
  val prevOutputTxIds = transaction.inputs.map(_.previousOutput.txId)
  val noDuplicateInputs = prevOutputTxIds.distinct.size == prevOutputTxIds.size
\end{lstlisting}
It gathers all inputs output transaction ids.
On this previous outputs ids it calls distinct and checks if the size stays the same.
Distinct removes duplicates, so if there was two times the same input transaction id the size of those ids would be greater before calling distinct.
